The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)

### 2018-12-03 analysis/paper/paper.Rmd
fix mean.plot problem

aov_thickness <- aoa.test(techno_data, "Thickness")
cohens_thickness <- cohens.test(aov_thickness)
aov_thickness <-  tidy(aov_thickness)

@@

area <- mean.plot(techno_data, "Chronology", "Area", "RawMaterial")
thickness <- mean.plot(techno_data, "Chronology", "Thickness", "RawMaterial")

>>>>

aov_thickness <- aov.test(techno_data, "Thickness")
cohens_thickness <- cohens.test(aov_thickness)
aov_thickness <-  tidy(aov_thickness)

@@

area <- mean..bar.plot(techno_data, "Chronology", "Area", "RawMaterial")
thickness <- mean..bar.plot(techno_data, "Chronology", "Thickness", "RawMaterial")
